\documentclass[main.tex]{subfiles}
\begin{document}
%\begin{fullwidth}
\selectlanguage{hebrew}
%\begin{changemargin}{3cm}{3cm}
\begin{center}
\LARGE{\textbf{שלוםק}}
\end{center}
\vspace{15px}
היפופוטם ננסי הוא יונק גדול, בן למשפחת ההיפופוטמיים, אנדמי ליערות ולביצות במערב אפריקה. אוכלוסיית ההיפו הגמדי הגדולה ביותר נמצאת בליבריה. הוא היצור החי הקרוב ביותר להיפופוטם. ההיפו הגמדי מותאם היטב לחיים ביבשה, אך בדומה לבן דודו הענק, הוא מימי-למחצה, כלומר מסתמך על קרבה למקור מים על מנת לשמור על לחות עורו ועל קור גופו. התנהגויות מסוימות, כמו הזדווגות והמלטת גורים, עשויות להתרחש במים או ביבשה. ההיפו הגמדי הוא בעל חיים מתבודד ופעיל לילה, צמחוני.

ההיפו הגמדי נדיר למדי. עד המאה ה-19 הוא לא היה ידוע מחוץ למערב אפריקה. ההיפו מתרבה היטב בשבי, ולכן מרבית המחקר אודותיו נעשה בגני חיות. בבר, לעומת זאת, מצבו של ההיפו מזהיר פחות: איגוד השימור העולמי מעריך כי בטבע נשארו פחות מ-3,000 פרטים. האיום העיקרי על אוכלוסיות ההיפו הוא אובדן בתי גידול, שכן היערות מבוראים במהירות. איומים משניים יותר מגיעים מצדם של ציידים, טורפים טבעיים ומלחמות האדם. 
\selectlanguage{english}
\begin{center}
\LARGE{\textbf{Abstract}}
\end{center}
\large{
Research of plasma parameters obtained by controlled discharge in 3D printed gas filled capillaries, are presented. The obtained results have implications to the laser wakefield acceleration (LWFA) scheme.

We demonstrate a synchronization capability in the scale of 1 ns using straight and curved capillaries. 

This high precision opens a hatch into the possibility of sufficient synchronization between three systems -- synchronization between the plasma generation, the incident ultra-short high intensity laser and the injection of the electrons.

We also demonstrate the formation of a plasma channel in the  capillary, resulting optical guiding, with an 84 MHz Ti:Sa oscillator laser, for the purpose of extending the propagation distances of intense laser pulses over many Rayleigh lengths, in a "fish--bone" scheme.

The verification of a preformed plasma channel with a hollow, parabolic plasma density profile using a temporally resolved plasma spectroscopy measurement is also presented.
}
%\end{changemargin}
%\end{fullwidth}
\end{document}